A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-08-14 tidyindex.qmd
various small changes

\begin{equation}
\begin{aligned}
x^l(s;t) = [x^1(s;t), x^2(s;t), & \cdots, x^L(s;t)] \\
& l = 1, 2, \cdots L, s \in D_s \subseteq \mathbb{R}^d, t \in D_t \subseteq \mathbb{R}^m 
\end{aligned}
\end{equation}

where $x^l$ is the $l$th variable, $s$ is the spatial location, and $t$ is the temporal order. <!-- We assume the spatial and temporal indexes do not depend on the variable, that is, all the variables share the same set of spatial and temporal indexes.--> The spatial space, $D_s \subseteq \mathbb{R}^d$, is generic to include different spatial representations, including a 1D set of $n$ locations $\{D_s: s_1, s_2, \cdots, s_n\}$, a 2D set of longitude and latitude pairs, and $d$-D coordinate set. The higher dimension in the temporal space, $D_t \subseteq \mathbb{R}^m$, can be used to represent for a $m$-D deconstruction of time. For example, a year-month combination, $(Y, M)^\prime$, can be used to record monthly precipitation series from January 1990 to December 2020, where $Y = 1990, \cdots, 2020$ and $M = 1, \cdots, 12$. In the case when the spatial dimension is fixed, multivariate temporal data can be simplified as $x^l_s(t)$, and similarly,  multivariate spatial data can be simplified as $x^l_t(s)$.

@@

`Input`: $x^l_s(t)$,

@@

```{r cache=TRUE, echo = TRUE, message=FALSE}
.scale <- c(6, 12, 24, 36)
idx <- queensland %>%
  init(id = id, time = ym) %>%
  compute_indexes(
    spei = idx_spei(
      .pet_method = "thornthwaite", .tavg = tavg, .lat = lat,
      .scale = .scale, .dist = c(gev(), loglogistic())),
    spi = idx_spi(.scale = .scale)
  )
```

@@

```{r fig-compute-spatial}
#| fig-cap: "Spatial distribution of Standardized Precipitation Index (SPI-12) in Queensland, Australia during two major flood and drought events: 2010/11 and 2019/20. The map shows a continous wet period during the 2010/11 flood period and a mitigated drought situation, after its worst in 2019 December and 2020 Janurary, likely due to the increased rainfall in February from the meteorological record."
#| fig-width: 12
#| fig-height: 5
queensland_map <- ozmaps::abs_ste %>% filter(NAME == "Queensland") %>% 
  rmapshaper::ms_simplify(keep = 0.02)
queensland_map %>%
  ggplot() +
  geom_sf(fill = "transparent", color = "grey50", linewidth = 0.4) +
  geom_point(
    data = idx %>%
      filter(.idx == "spi", .scale == 12) %>%
      filter(((year(ym) %in% c(2010, 2019) & month(ym) >= 10) )|
               ((year(ym) %in% c(2011, 2020) & month(ym) <= 3) )), 
    aes(x = long, y = lat, color = .index)) +
  colorspace::scale_color_continuous_divergingx(palette = "Geyser", rev = TRUE, name = "Index") + 
  theme_void() +
  facet_wrap(vars(ym), ncol = 6)
```

```{r fig-compute-temporal}
#| fig-cap: 'Time series plot of Standardized Precipitation-Evapotranspiration Index (SPEI) at the Texas post office station (highlighted by a diamond shape in panel a). The SPEI is calculated at four time scales (6, 12, 24, and 36 months) and fitted with two distributions (Log Logistic and GEV). The dashed line at -2 represents the class "extreme drought" by the SPEI. A larger time scale gives a smoother index series, while also takes longer to recover from an extreme situation as seen in the  2019/20 drought period. The SPEI values from two distribution fits mostly agree, while GEV can results in more extreme values, i.e. in 1998 and 2020.'
#| fig-width: 12
#| fig-height: 6
texas <- idx %>%
    filter(name == "TEXAS POST OFFICE", .idx == "spei") %>% distinct(long, lat)
p1 <- queensland_map %>%
  ggplot() +
  geom_sf(fill = "transparent") +
  geom_point(data = queensland %>%
               distinct(id, long, lat, name),
             aes(x = long, y = lat)) +
  geom_point(data = texas, aes(x = long, y = lat),
             color = "orange", shape = 18, fill = "orange", size = 4) +  
  theme_void()

@@

(p1 | p2)  + 
  patchwork::plot_annotation(tag_levels = "a") + 
  patchwork::plot_layout(guides = "collect")  &
  theme(legend.position = "bottom")

@@

The result can be compared with the GGGI values available in the report as shown in @fig-compare-gggi, validating the reproducibility of the index for country with no missing variables.

@@

dt2 <- gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight))

dt2$data %>%
  filter(!is.na(index_new)) %>% 
  ggplot(aes(x = index, y = index_new)) +
  geom_abline(slope = 1, intercept = 0, color = "grey") + 
  geom_point() +
  theme_bw() + 
  theme(aspect.ratio = 1, panel.grid.minor = element_blank()) + 
  xlab("Benchmark") + 
  ylab("Index calculated")
```

@@

To understand the uncertainty of this dimension reduction step from combining four dimensions (Economy, Education, Health, and Politics), we run a local tour [TODO: reference to local tour] that varies the weight of each dimension slightly to observe how index value and country ranking changes. The local tour produces an animation that gradually increases the weight of one variable and reduces it back to equal weight, one at a time. A set of countries are selected for this exercise, which includes 1) the top four with GGGI > 0.85, 2) a set of countries with GGGI between 0.72 and 0.73 (Brazil, Panama, Poland, Bangladesh, Kazakhstan, Armenia, and Slovakia), and 3) the bottom five countries with GGGI < 0.6. Five frames (equal weights and one for each dimension with a relatively higher weight) are selected from the local tour animation to show in @fig-idx-tour and the full animation is available at  https://vimeo.com/847874016?share=copy.

@@

```{r fig-idx-tour, fig.align='center', fig.height=5} 
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at https://vimeo.com/847874016?share=copy."  
#frames <- c("001", "013", "037", "061", "085", "109")
frames <- c("001", "006", "012", "018", "024", "029")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 3)  
```

>>>>

\begin{equation}
\begin{aligned}
\mathbf{x}(s;t) = [x^1(s;t), x^2(s;t), & \cdots, x^P(s;t)] \\
& p = 1, 2, \cdots P, s \in D_s \subseteq \mathbb{R}^d, t \in D_t \subseteq \mathbb{R}^m 
\end{aligned}
\end{equation}

where $x^l$ is the $p$th variable, $s$ is the spatial location, and $t$ is the temporal order. <!-- We assume the spatial and temporal indexes do not depend on the variable, that is, all the variables share the same set of spatial and temporal indexes.--> The spatial space, $D_s \subseteq \mathbb{R}^d$, is generic to include different spatial representations, including a 1D set of $n$ locations $\{D_s: s_1, s_2, \cdots, s_n\}$, a 2D set of longitude and latitude pairs, and $d$-D coordinate set. The higher dimension in the temporal space, $D_t \subseteq \mathbb{R}^m$, can be used to represent for a $m$-D deconstruction of time. For example, a year-month combination, $(Y, M)^\prime$, can be used to record monthly precipitation series from January 1990 to December 2020, where $Y = 1990, \cdots, 2020$ and $M = 1, \cdots, 12$.  To simplify the notation, a subscript letter $s$ or $t$ is used to denote the data have a fixed spatial locations or temporal order. When the spatial locations are fixed, the data become multivariate time series, denoted as $x^l_s(t)$. Similarly,  $x^l_t(s)$ represents multivariate spatial data when the temporal dimension is fixed.

@@

`Input`: $x_s(t)$,

@@

```{r cache=TRUE, echo = TRUE, message=FALSE, eval=FALSE}
.scale <- c(6, 12, 24, 36)
idx <- queensland %>%
  init(id = id, time = ym) %>%
  compute_indexes(
    spei = idx_spei(
      .pet_method = "thornthwaite", .tavg = tavg, .lat = lat, 
      .scale = .scale, .dist = c(gev(), loglogistic())),
    spi = idx_spi(.scale = .scale)
  )
```

```{r eval = FALSE}
save(idx, file = here::here("data/idx.rda"))
```

@@

```{r fig-compute-spatial}
#| fig-cap: "Spatial distribution of Standardized Precipitation Index (SPI-12) in Queensland, Australia during two major flood and drought events: 2010/11 and 2019/20. The map shows a continous wet period during the 2010/11 flood period and a mitigated drought situation, after its worst in 2019 December and 2020 Janurary, likely due to the increased rainfall in February from the meteorological record."
#| fig-width: 6
load(here::here("data/idx.rda"))
queensland_map <- ozmaps::abs_ste %>% filter(NAME == "Queensland") %>% 
  rmapshaper::ms_simplify(keep = 0.02)
queensland_map %>%
  ggplot() +
  geom_sf(fill = "transparent", color = "grey50", linewidth = 0.4) +
  geom_point(
    data = idx %>%
      filter(.idx == "spi", .scale == 12) %>%
      filter(((year(ym) %in% c(2010, 2019) & month(ym) >= 10) )|
               ((year(ym) %in% c(2011, 2020) & month(ym) <= 3) )), 
    aes(x = long, y = lat, color = .index)) +
  colorspace::scale_color_continuous_divergingx(palette = "Geyser", rev = TRUE, name = "Index") + 
  theme_void() +
  facet_wrap(vars(ym), ncol = 6)
```

```{r fig-compute-temporal}
#| fig-cap: 'Time series plot of Standardized Precipitation-Evapotranspiration Index (SPEI) at the Texas post office station (highlighted by a diamond shape in panel a). The SPEI is calculated at four time scales (6, 12, 24, and 36 months) and fitted with two distributions (Log Logistic and GEV). The dashed line at -2 represents the class "extreme drought" by the SPEI. A larger time scale gives a smoother index series, while also takes longer to recover from an extreme situation as seen in the  2019/20 drought period. The SPEI values from two distribution fits mostly agree, while GEV can results in more extreme values, i.e. in 1998 and 2020.'
#| fig-width: 8
#| fig-height: 5
texas <- idx %>%
    filter(name == "TEXAS POST OFFICE", .idx == "spei") %>% distinct(long, lat)
p1 <- queensland_map %>%
  ggplot() +
  geom_sf(fill = "transparent") +
  geom_point(data = queensland %>%
               distinct(id, long, lat, name),
             aes(x = long, y = lat)) +
  geom_point(data = texas, aes(x = long, y = lat),
             color = "orange", shape = 18, fill = "orange", size = 4) +  
  theme_void()

@@

(p1 | p2)  + 
  patchwork::plot_annotation(tag_levels = "a") + 
  patchwork::plot_layout(guides = "collect", widths = c(1, 4))  &
  theme(legend.position = "bottom")

@@

The result can be compared with the GGGI values available in the report, validating the reproducibility of the index for country with no missing variables.

@@

dt2 <- gggi %>% 
  init(id = country) %>%
  add_meta(gggi_weights, var_col = variable) %>% 
  dimension_reduction(
    index_new = aggregate_linear(
      ~labour_force_participation:years_with_female_head_of_state,
      weight = weight)) 
```

@@

To understand the uncertainty of this dimension reduction step from combining four dimensions (Economy, Education, Health, and Politics), we run a local tour [TODO: reference to local tour] that varies the weight of each dimension slightly to observe how index value and country ranking changes. The local tour produces an animation that gradually increases the weight of one variable and reduces it back to equal weight, one at a time. A set of countries are selected for this exercise, which includes 1) the top four with GGGI > 0.85, 2) a set of countries with GGGI between 0.72 and 0.73 (Brazil, Panama, Poland, Bangladesh, Kazakhstan, Armenia, and Slovakia), and 3) the bottom five countries with GGGI < 0.6. Five frames (equal weights and one for each dimension with a relatively higher weight) are selected from the local tour animation to show in @fig-idx-tour and the full animation is available at  https://vimeo.com/847874016.

@@

```{r fig-idx-tour, fig.align='center', fig.height=5} 
#| fig-cap: "Five frames selected from varying the linear weights of four dimensions in Global Gender Gap Index. The weights vary slightly from the official simple average weights (0.25, 0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full animation is available at https://vimeo.com/847874016."  
#frames <- c("001", "013", "037", "061", "085", "109")
frames <- c("001", "006", "012", "018", "024", "029")
ani <- paste0(here::here("figures/"), "idx-tour/", "idx-tour-", frames, ".png")
rl <- lapply(ani, png::readPNG)
gl <-  lapply(rl, grid::rasterGrob)
wrap_plots(gl, ncol = 3)  
```

### 2023-08-14 tidyindex.tex
various small changes

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, frame hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{equation}
\begin{aligned}
x^l(s;t) = [x^1(s;t), x^2(s;t), & \cdots, x^L(s;t)] \\
& l = 1, 2, \cdots L, s \in D_s \subseteq \mathbb{R}^d, t \in D_t \subseteq \mathbb{R}^m 
\end{aligned}
\end{equation}

where \(x^l\) is the \(l\)th variable, \(s\) is the spatial location,
and \(t\) is the temporal order. The spatial space,
\(D_s \subseteq \mathbb{R}^d\), is generic to include different spatial
representations, including a 1D set of \(n\) locations
\(\{D_s: s_1, s_2, \cdots, s_n\}\), a 2D set of longitude and latitude
pairs, and \(d\)-D coordinate set. The higher dimension in the temporal
space, \(D_t \subseteq \mathbb{R}^m\), can be used to represent for a
\(m\)-D deconstruction of time. For example, a year-month combination,
\((Y, M)^\prime\), can be used to record monthly precipitation series
from January 1990 to December 2020, where \(Y = 1990, \cdots, 2020\) and
\(M = 1, \cdots, 12\). In the case when the spatial dimension is fixed,
multivariate temporal data can be simplified as \(x^l_s(t)\), and
similarly, multivariate spatial data can be simplified as \(x^l_t(s)\).

@@

\texttt{Input}: \(x^l_s(t)\),

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{.scale }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{36}\NormalTok{)}
\NormalTok{idx }\OtherTok{\textless{}{-}}\NormalTok{ queensland }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{init}\NormalTok{(}\AttributeTok{id =}\NormalTok{ id, }\AttributeTok{time =}\NormalTok{ ym) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{compute\_indexes}\NormalTok{(}
    \AttributeTok{spei =} \FunctionTok{idx\_spei}\NormalTok{(}
      \AttributeTok{.pet\_method =} \StringTok{"thornthwaite"}\NormalTok{, }\AttributeTok{.tavg =}\NormalTok{ tavg, }\AttributeTok{.lat =}\NormalTok{ lat,}
      \AttributeTok{.scale =}\NormalTok{ .scale, }\AttributeTok{.dist =} \FunctionTok{c}\NormalTok{(}\FunctionTok{gev}\NormalTok{(), }\FunctionTok{loglogistic}\NormalTok{())),}
    \AttributeTok{spi =} \FunctionTok{idx\_spi}\NormalTok{(}\AttributeTok{.scale =}\NormalTok{ .scale)}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] "Checking for missing values (`NA`): all the data must be complete. Input type is vector. Assuming the data are monthly time series starting in January, all regular (non-leap) years."
\end{verbatim}

@@

The result can be compared with the GGGI values available in the report
as shown in Figure~\ref{fig-compare-gggi}, validating the
reproducibility of the index for country with no missing variables.

{\centering \includegraphics{tidyindex_files/figure-pdf/fig-compare-gggi-1.pdf}

\caption{\label{fig-compare-gggi}Verifying the calculation of the Global
Gender Gap Index (GGGI). The index can be reproduced from the
methodology described in the Global Gender Gap Report 2023 after
removing the countries with missing variables, the treatment of which is
unclear.}

To understand the uncertainty of this dimension reduction step from
combining four dimensions (Economy, Education, Health, and Politics), we
run a local tour {[}TODO: reference to local tour{]} that varies the
weight of each dimension slightly to observe how index value and country
ranking changes. The local tour produces an animation that gradually
increases the weight of one variable and reduces it back to equal
weight, one at a time. A set of countries are selected for this
exercise, which includes 1) the top four with GGGI \textgreater{} 0.85,
2) a set of countries with GGGI between 0.72 and 0.73 (Brazil, Panama,
Poland, Bangladesh, Kazakhstan, Armenia, and Slovakia), and 3) the
bottom five countries with GGGI \textless{} 0.6. Five frames (equal
weights and one for each dimension with a relatively higher weight) are
selected from the local tour animation to show in
Figure~\ref{fig-idx-tour} and the full animation is available at
https://vimeo.com/847874016?share=copy.

@@

\caption{\label{fig-idx-tour}Five frames selected from varying the
linear weights of four dimensions in Global Gender Gap Index. The
weights vary slightly from the official simple average weights (0.25,
0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full
animation is available at https://vimeo.com/847874016?share=copy.}

>>>>

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{equation}
\begin{aligned}
\mathbf{x}(s;t) = [x^1(s;t), x^2(s;t), & \cdots, x^P(s;t)] \\
& p = 1, 2, \cdots P, s \in D_s \subseteq \mathbb{R}^d, t \in D_t \subseteq \mathbb{R}^m 
\end{aligned}
\end{equation}

where \(x^l\) is the \(p\)th variable, \(s\) is the spatial location,
and \(t\) is the temporal order. The spatial space,
\(D_s \subseteq \mathbb{R}^d\), is generic to include different spatial
representations, including a 1D set of \(n\) locations
\(\{D_s: s_1, s_2, \cdots, s_n\}\), a 2D set of longitude and latitude
pairs, and \(d\)-D coordinate set. The higher dimension in the temporal
space, \(D_t \subseteq \mathbb{R}^m\), can be used to represent for a
\(m\)-D deconstruction of time. For example, a year-month combination,
\((Y, M)^\prime\), can be used to record monthly precipitation series
from January 1990 to December 2020, where \(Y = 1990, \cdots, 2020\) and
\(M = 1, \cdots, 12\). To simplify the notation, a subscript letter
\(s\) or \(t\) is used to denote the data have a fixed spatial locations
or temporal order. When the spatial locations are fixed, the data become
multivariate time series, denoted as \(x^l_s(t)\). Similarly,
\(x^l_t(s)\) represents multivariate spatial data when the temporal
dimension is fixed.

@@

\texttt{Input}: \(x_s(t)\),

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{.scale }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{, }\DecValTok{12}\NormalTok{, }\DecValTok{24}\NormalTok{, }\DecValTok{36}\NormalTok{)}
\NormalTok{idx }\OtherTok{\textless{}{-}}\NormalTok{ queensland }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{init}\NormalTok{(}\AttributeTok{id =}\NormalTok{ id, }\AttributeTok{time =}\NormalTok{ ym) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{compute\_indexes}\NormalTok{(}
    \AttributeTok{spei =} \FunctionTok{idx\_spei}\NormalTok{(}
      \AttributeTok{.pet\_method =} \StringTok{"thornthwaite"}\NormalTok{, }\AttributeTok{.tavg =}\NormalTok{ tavg, }\AttributeTok{.lat =}\NormalTok{ lat, }
      \AttributeTok{.scale =}\NormalTok{ .scale, }\AttributeTok{.dist =} \FunctionTok{c}\NormalTok{(}\FunctionTok{gev}\NormalTok{(), }\FunctionTok{loglogistic}\NormalTok{())),}
    \AttributeTok{spi =} \FunctionTok{idx\_spi}\NormalTok{(}\AttributeTok{.scale =}\NormalTok{ .scale)}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

@@

The result can be compared with the GGGI values available in the report,
validating the reproducibility of the index for country with no missing
variables.

To understand the uncertainty of this dimension reduction step from
combining four dimensions (Economy, Education, Health, and Politics), we
run a local tour {[}TODO: reference to local tour{]} that varies the
weight of each dimension slightly to observe how index value and country
ranking changes. The local tour produces an animation that gradually
increases the weight of one variable and reduces it back to equal
weight, one at a time. A set of countries are selected for this
exercise, which includes 1) the top four with GGGI \textgreater{} 0.85,
2) a set of countries with GGGI between 0.72 and 0.73 (Brazil, Panama,
Poland, Bangladesh, Kazakhstan, Armenia, and Slovakia), and 3) the
bottom five countries with GGGI \textless{} 0.6. Five frames (equal
weights and one for each dimension with a relatively higher weight) are
selected from the local tour animation to show in
Figure~\ref{fig-idx-tour} and the full animation is available at
https://vimeo.com/847874016.

@@

\caption{\label{fig-idx-tour}Five frames selected from varying the
linear weights of four dimensions in Global Gender Gap Index. The
weights vary slightly from the official simple average weights (0.25,
0.25, 0.25, 0.25) to observe how the index and ranking reponse. Full
animation is available at https://vimeo.com/847874016.}
